---
title       : Slidify Shiny Application project
subtitle    : Toothgrowth analysis
author      : LonePine 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 1

1. Exploratory analysis on Toothgrowth data in the R datasets package
2. Load the datasets package in R and then load the ToothGrowth data
3. The response is the length of teeth in each of 10 guinea pigs. 

--- .class #id 

## Slide 2

1. Each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid) is administered.
2.
library(datasets)
library(plyr)
help(ToothGrowth)
## starting httpd help server ... done
dim(ToothGrowth)
## [1] 60  3

---

## Slide 3

1. ```{r, echo=TRUE}
summary(ToothGrowth)
```
---

## Slide 4

```{r, echo=TRUE}
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth, xlab = "ToothGrowth data: length Vs dose, given type of supplement", col = "blue")
```

---

## Slide 5

```{r, echo=FALSE}
hist(ToothGrowth$len, col = "Yellow")
abline(v = median(ToothGrowth$len),col = "blue", lwd = 4 )

```



